Draft_Application_Stochastic_Volatility

### 2021-07-16 Real Dataset SV.Rmd
aggiunta introduzione

output:
  pdf_document: 
   latex_engine: xelatex
   fig_width: 5
   fig_height: 3.5
   fig_caption: true
   extra_dependencies: ["float"]
   number_sections: true 
---
\section{Overview}
In the following sections, we will try to replicate some of the analyses which were previously conducted on synthetic data, generated by a basic stochastic volatility model; this time, the same model specification and filters will be used on real data. However, as we will see, real data require different strategies to evaluate the effectiveness of several Sequential Monte Carlo techniques. Intuitively, such differences are due to the fact that now the latent process driving the Hidden Markov Model is not observed, nor do we know exactly its law of motion. 
This part of the work is structured as follows:

@@

In section (\textit{fill with the number of the section}) a simple specification of a Stochastic Volatility model was presented and used as the data generating process of a simulated dataset. Denoting by $y_t$ the log returns at time $t$ and by $x_t$ the latent volatility stochastic process, such state-space model was presented as follows, 
\begin{align*}
    y_t|x_t & \sim N(0,e^{x_t})\\
    x_t|x_{t-1},\alpha,\beta,\tau^2 & \sim N(\alpha+\beta x_{t-1},\tau^2)
\end{align*}

@@

\end{align*} where the error terms $u_t$ and $\eta_t$ are independent across all leads and lags, while $\nu_t$ follows an unspecified time-varying process.\

@@

As regards the series that we will employ in section (\textit{fill with the number of the section}), namely the series of realised volatilities which we will employ as a proxy for the true latent volatilities, the data were retrieved from the Oxford-Man Institute's Realized Library, which provides several different daily non-parametric measures of past volatility. We consider a proper rescaling of the \textit{rv5} series, \textit{i.e.} model-free daily volatility estimates based on 5 min intraday return intervals. Also in this case, the chosen interval spanned from June 1st, 2017 to May 30th, 2021. \textit{Includere grafico e commento del grafico della realised volatility}

>>>>

output:
  pdf_document: 
   latex_engine: xelatex
   fig_width: 5
   fig_height: 3.5
   fig_caption: true
   extra_dependencies: ["float"]
   number_sections: true 
---

\section{Overview}
In the following sections, we will try to replicate some of the analyses which were previously conducted on synthetic data, generated by a basic stochastic volatility model; this time, the same model specification and filters will be used on real data. However, as we will see, real data require different strategies to evaluate the effectiveness of several Sequential Monte Carlo techniques. Intuitively, such differences are due to the fact that now the latent process driving the Hidden Markov Model is not observed, nor do we know exactly its law of motion. 
This part of the work is structured as follows: section \textit{fill with the number of the section} provides a review of recent research in the stochastic volatility literature, including extensions of the basic specification and the use of particle filters; section \textit{fill with the number of the section} describes the data which we employ and the transformations that were applied on them. In section \textit{fill with the number of the section} several particle filters are compared in terms of computational cost in approximating the filtering distribution implied by our SV model. Section \textit{fill with the number of the section} features a forecast comparison between two SV specifications and a model that assumes constant mean and variance for the financial returns, namely a forecasting exercise that would not be possible were it not for particle filtering techniques. In section \textit{fill with the number of the section} we conclude by employing a non-parametric measure of realised volatility as a proxy for the latent volatility process, allowing a RMSE and MAE comparison between filters which is similar to that of section \textit{fill with the number of the section} for synthetic data.

@@

In section \textit{fill with the number of the section} a simple specification of a Stochastic Volatility model was presented and used as the data generating process of a simulated dataset. Denoting by $y_t$ the log returns at time $t$ and by $x_t$ the latent volatility stochastic process, such state-space model was presented as follows, 
\begin{align*}
    y_t|x_t & \sim N(0,e^{x_t})\\
    x_t|x_{t-1},\alpha,\beta,\tau^2 & \sim N(\alpha+\beta x_{t-1},\tau^2)
\end{align*}

@@

where the error terms $u_t$ and $\eta_t$ are independent across all leads and lags, while $\nu_t$ follows an unspecified time-varying process.\

@@

As regards the series that we will employ in section \textit{fill with the number of the section}, namely the series of realised volatilities which we will employ as a proxy for the true latent volatilities, the data were retrieved from the Oxford-Man Institute's Realized Library, which provides several different daily non-parametric measures of past volatility. We consider a proper rescaling of the \textit{rv5} series, \textit{i.e.} model-free daily volatility estimates based on 5 min intraday return intervals. Also in this case, the chosen interval spanned from June 1st, 2017 to May 30th, 2021. \textit{Includere grafico e commento del grafico della realised volatility}

\subsection{Transformations}
Inserire le trasformazioni effettuate (e il perchè)
